% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}

\usepackage[spanish]{babel}
\usepackage{verbatim}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Mauricio Carrillo Valencia}
\newcommand{\CVTitle}{M. Carrillo CV IFM}
\newcommand{\CVNote}{CV compiled on {\today} for IFM-UMSNH}
\newcommand{\CVWebpage}{http://www.example.com/~johndoe}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
%pdfproducer={},
pdfkeywords={},
unicode=true,
%bookmarks=true,
%bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks
}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

%\begin{SubTitle}
%\href{https://www.google.com/maps/place/17+Prime+Avenue,+Springfield,+Pennsylvania+10111,+USA}
%{Franciso Aguiar y Seijas, 195, Morelia, Michoac\'an, 52700. M\'exico.}
%\par
%\href{mailto:mcarrillo@ifm.umich.mx}
%{mcarrillo@ifm.umich.mx}
%\,\SubBulletSymbol\,
%+52\,(443)\,440-6056
%\,\SubBulletSymbol\,
%\href{\CVWebpage}
%{\url{\CVWebpage}}
%\end{SubTitle}

\begin{Body}

\Gap

%%%%%%%%%%%%%%%%%%%%%%%
%%%%  INFORMATION  %%%%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Personal Information}
{Personal Information}
{PDF:Personal Information}

\Entry
%\href{http://www.ifm.umsnh.mx/}
Francisco Aguiar y Seijas 195, \\
Fray Antonio de San Miguel Iglesias, \\
Morelia, Michoac\'an, 58277, M\'exico
\Entry
{+52 (443) 440-6056}
\Entry
\href{mailto:mcarrillo@ifm.umich.mx}
{mcarrillo@ifm.umich.mx}
\Entry
\href{mailto:carrillo.valenciam@gmail.com}
{carrillo.valenciam@gmail.com}




%%%%%%%%%%%%%%%%%%%%%%%
%%%% OFFICE  INFORMATION  %%%%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Institutional Information}
{Institutional Information}
{PDF:Institutional Information}

\Entry
%\href{http://www.ifm.umsnh.mx/}
Instituto de F\'isica y Matem\'aticas, \\
Universidad Michoacana de San Nicol\'as de Hidalgo, \\
Francisco J. M\'ugica S/N, Ciudad Universitaria, edificio C-3, \\
Morelia, Michoac\'an, 58030, M\'exico
\Entry
{+52 (443) 322-3500, ext. 4140}
\Entry
\href{www.ifm.umich.mx}
{www.ifm.umich.mx}
\Entry


\Gap

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{http://www.ifm.umich.mx/}
{\textbf{Universidad Michoacana de San Nicol\'as de Hidalgo. \\
Instituto de F\'isica y Matem\'aticas.}} \\
Morelia, Michoac\'an, M\'exico

\Gap
\BulletItem
Ph.D. student in
%\href{http://www.example.com/my-department}
{Physics} 
\hfill 
\DatestampYMD{2013}{09}{01} -- (Expected Date)
\DatestampYMD{2017}{08}{30}

%\begin{Detail}
\Gap
\Item
Thesis:
%\href{http://www.example.com/my-phd-thesis}
{Artificial Neural Networks Applied to Inverse Problems in Physics.}
\Item
Adviser:
Dr.~Jos\'e~ Antonio Gonz\'alez Cervera
\Item
Summary:
Machine Learning programming. Artificial neural networks applied to parameter estimation in simulated gravitational waves of binary black hole collision. Characterization and classification of fluid patterns in simulated fluid dynamics.
%\end{Detail}

\Gap
\BulletItem
M.Sc. in
%\href{http://www.example.com/my-department}
{Physics}
\hfill
\DatestampYMD{2011}{03}{01} --
\DatestampYMD{2013}{06}{28}

%\begin{Detail}
\Gap
\Item
Thesis: Action Potencial Backpropagation: A Simulation Study of the Participation of Ionic Channel Kv4.2
\Item
Adviser:
Dr.~Jos\'e~ Antonio De Santiago Castillo
\Item
Summary: Biophysics. Action potential simulation, modelling ionic channels currents using differential equations and Markov Chains formalism with an object-oriented programming approach.
%\end{Detail}

\BigGap
\Entry
\href{http://www.uaemex.mx}
{\textbf{Universidad Aut\'onoma del Estado de M\'exico.}}\\
Toluca, Estado de M\'exico, M\'exico

\Gap
\BulletItem
B.Sc. in
%\href{http://www.example.com/my-department}
{Physics}
\hfill
\DatestampYMD{2003}{03}{01} --
\DatestampYMD{2008}{05}{15}

%\begin{Detail}
\Gap
\Item
Thesis: A Study of Solitonic Structures in DNA's Vibrational Dynamics.
\Item
Adviser:
Dr.~Maximo Ag\"uero Granados
\Item
Summary: Mathematical description and solitonic solutions of DNA's vibrational dynamics under Peyrard-Bishop model.
%\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

%\Section
%{Research Experience}
%{Research Experience}
%{PDF:ResearchExperience}

%\Entry
%\href{http://www.example.com/my-institute}
%{\textbf{Institute for Advanced Research}},
%Science College

%\Gap
%\BulletItem
%Undergraduate Research Student, Science Department
%\hfill
%\DatestampYMD{2004}{05}{15} --
%\DatestampYMD{2005}{05}{15}
%\begin{Detail}
%\SubBulletItem
%Project:
%Investigations on the Use of Lasers to Measure Climate Change
%\SubBulletItem
%Supervisors:
%Prof.~Jane~Citizen and
%Dr~Ann~Yone
%\SubBulletItem
%Focus:
%Climate change, lasers, statistical analysis, data analytics.
%\end{Detail}

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

\SubSection
{Journals}
{Journals}
{PDF:Journals}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
%\renewcommand{\MaxNumberedItem}{[88]}

\Gap
\NumberedItem{[1]}
\href{https://doi.org/10.1016/j.commatsci.2017.04.030}
{\underline{M.~Carrillo}, J.~A.~Gonz\'alez, C.~L\'opez and A. Raya
``Bloch oscillations in a two-dimensional crystals: Inverse problem'',
\textit{Computational Materials Science, Elsevier},
vol.~137,
%no.~4,
pp.~1--5,
\DatestampYM{2017}{09}.}


\Gap
\NumberedItem{[2]}
\href{https://doi.org/10.1103/PhysRevE.94.063304}
{\underline{M.~Carrillo}, U.~Salinas and J.~A.~Gonz\'alez
``Estimation of the Reynolds number for flows around a cylinders with lattice Boltzmann methods and artificial neural networks'',
\textit{Phys. Rev. E},
vol.~12,
no.~4,
pp.~330--352,
\DatestampYM{2016}{12}.}

\Gap
\NumberedItem{[3]}
\href{https://link.springer.com/article/10.1007/s10714-016-2136-0}
{\underline{M.~Carrillo}, M.~Gracia, J.~A.~Gonz\'alez and F.~Guzm\'an
``Parameter estimates in binary black hole collisions using neural networks'',
\textit{Gen. Rel. Grav.},
vol.~12,
no.~4,
pp.~330--352,
\DatestampYM{2016}{09}.}

\Gap
\NumberedItem{[4]}
\href{http://dx.doi.org/10.1142/S021797920803968X}
{M.~A.~Ag\"uero, M.~De Lourdes Najera, and \underline{M.~Carrillo},
``Nonclassic solitonic structures in DNA's vibrational dynamics'',
\textit{Int. J. Mod. Phys. B},
vol.~22,
no.~16,
pp.~2571--2582,
\DatestampYM{2008}{06}.}

\endgroup

\BigGap

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% ACCEPTED PAPERS %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\SubSection
%{Accepted Papers}
%{Accepted Papers}
%{PDF:Accepted Papers}

%\begingroup


%\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% SUBMITTED PAPERS %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%


\SubSection
{Submitted Papers}
{Submitted Papers}
{PDF:Submitted Papers}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
%\renewcommand{\MaxNumberedItem}{[88]}

\BigGap
\NumberedItem{[1]}
%\href{http://www.example.com/my-paper-doi-4}
{\underline{M.~Carrillo}, C.~L\'opez, J.~A.~Gonz\'alez and U.~Salinas
``Estimation of an obstruction in a flow with artificial neural networks'', Submitted to:
\textit{Phys. Rev. E}}

\endgroup


\SubSection
{Proceedings}
{Proceedings}
{PDF:Proceedings}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
%\renewcommand{\MaxNumberedItem}{[8888]}

\Gap
\NumberedItem{[1]}
\href{http://iopscience.iop.org/article/10.1088/1742-6596/792/1/012071/meta}
{\underline{M.~Carrillo}, U.~Salinas and J.~A.~Gonz\'alez,
``Estimation of the Reynolds number in a Poiseuille flow using artificial neural networks'',
in \textit{Proceedings of the VIII International Congress of Engineering Physics},
M\'erida, Yucat\'an, M\'exico,
\DatestampYM{2016}{11}.}

%\Gap
%\NumberedItem{[2]}
%\href{http://www.example.com/my-paper-doi-2}
%{\underline{M.~Carrillo} and J.~A.~Gonz\'alez,
%``Artificial Neural Networks in USD/MXN Exchange Rate,''
%in \textit{Workshop and Time Series Analysis},
%Cuernavaca, Morelos, M\'exico,
%\DatestampYM{2015}{8}.}

\Gap
\NumberedItem{[2]}
\href{doi:10.1088/1742-6596/654/1/012001}
{\underline{M.~Carrillo}, J.A.~Gonz\'alez, M.~Gracia-Linares and F.~S.~Guzm\'an,
``Time series analysis of Gravitational Waves signals using neural networks'',
in \textit{Proceedings of the X Mexican School on Gravitation and Mathematical Physics}, Playa del Carmen, Quintana Roo, M\'exico,
\DatestampYM{2014}{12}.}

\endgroup

%%%%%%%%%%%%%%%%%%
%% TALKS %%
%%%%%%%%%%%%%%%%%%

\Section
{Talks}
{Talks}
{PDF:Talks}


\Entry
\BulletItem
{\textit{Time series analysis with neural networks: some examples},
Workshop for Time Series and Correlation Analysis,
Cuernavaca, Morelos, M\'exico,
\DatestampYM{2015}{8}.}

\Entry
\BulletItem
{\textit{An\'alisis de series de tiempo mediante redes neuronales}, Universidad TecMilenio,
Morelia, Michoac\'an, M\'exico,
\DatestampYM{2015}{8}.}



%%%%%%%%%%%%%%%
%% RESEARCH INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Research Interests}
{Research Interests}
{PDF:Research Interests}

\Entry
%{\TeX}, {\LaTeX}, {\XeLaTeX},
\BulletItem
Application and programming of Machine Learning methods (artificial neural networks, genetic algorithms, naive Bayes, etc.) and Statistical Programming for pattern recognition, data analysis and parameter inference for problems in Physics.% and Biophysics.

\Entry
%{\TeX}, {\LaTeX}, {\XeLaTeX},
\BulletItem
Signal \& Image Processing.

\Entry
\BulletItem
Computational Physics simulations.


%%%%%%%%%%%%%%%
%% LEARNING INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Learning Interests}
{Learning Interests}
{PDF:Learning Interests}

\Entry
\BulletItem
Deep learning. %and Bayesian methods.

\Entry
\BulletItem
Parallel programming with MPI and CUDA.
%Sentiment analysis with Machine Learning methods.
%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
Spanish: Native language.

\Gap
\BulletItem
English: Fluent (speaking, reading, writing).

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\BulletItem
C\# (advance),
Python (intermediate and learning),
R (intermediate and learning),
MATLAB (basic),
SQL (basic and learning),
Mathematica (basic),
Processing (basic).


\BulletItem
Others: 
Windows,
Linux,
IPython,
TensorFlow (basic and learning),
%GitHub,
LaTex,
Microsoft Word,
Microsoft Excel,
Microsoft PowerPoint.


%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests}
{Interests}
{PDF:Interests}

\Entry
\BulletItem
Photography,
writing,
reading,
cactux cultivation \&
swimming.


\newpage
%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%
\BigGap

\Section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Dr. Jos\'e Antonio Gonz\'alez Cervera}
\newline
Researcher \& Professor. \\
Instituto de F\'isica y Matem\'aticas,
\newline
Universidad Michoacana de San Nicol\'as de Hidalgo
\newline
\href{mailto:gonzalez@ifm.umich.mx}
{gonzalez@ifm.umich.mx}
%\,\SubBulletSymbol\,
%+52\,(443)\,123-3453

\BigGap
\BigGap

\BulletItem
\textbf{Dr. Francisco Guzm\'an Murillo}
\newline
Researcher \& Professor. \\
Instituto de F\'isica y Matem\'aticas, \newline
Universidad Michoacana de San Nicol\'as de Hidalgo.
\newline
\href{mailto:guzman@ifm.umich.mx}
{guzman@ifm.umich.mx}
%\,\SubBulletSymbol\,
%+52\,(443)\,123-3453


\BigGap
\BigGap

\BulletItem
\textbf{Dr. Jos\'e Antonio De Santiago Castillo}
\newline
CEO Reliotech and Former Researcher
\newline
Reliotech S.A.S. de C.V
%\newline
%San Luis Potos\'i, San Luis Potos\'i, M\'exico
\newline
\href{mailto:desantiago@reliotech.com}
{desantiago@reliotech.com}
%\,\SubBulletSymbol\,
%+52\,(444)\,123-3453


\begin{comment}
% Manual page break.
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% THIS IS A SECTION WITH USAGE NOTES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Declare a new group to limit the scope of \color to this section.
\begingroup
\color{red}

\Section
{This is a\newline
Section\newline
With\newline
Usage Notes}
{This is a Section With Usage Notes (For PDF Bookmark)}
{PDF:ThisIsASectionWithUsageNotes:ForPDFLink}

\SubSection
{This is a SubSection}
{This is a SubSection (For PDF Bookmark)}
{PDF:ThisIsASubSection:ForPDFLink}

\Gap
\BulletItem
Use \CodeCommand{Section\{a\}\{b\}\{c\}} and
\CodeCommand{SubSection\{a\}\{b\}\{c\}}
to create sections and subsections, where
\Code{a} is the heading displayed on the page,
\Code{b} is the PDF bookmark heading, and
\Code{c} is the internal PDF link (must be unique).
Sections and subsections will appear in the PDF bookmarks.
Note the CamelCase command names.

\Gap
\BulletItem
Use
\CodeCommand{Entry},
\CodeCommand{BulletItem},
\CodeCommand{SubBulletItem},
\CodeCommand{Item},
\CodeCommand{SubItem},
\CodeCommand{NumberedItem},
etc.,
to create entries in the main body of the CV.

\Gap
\BulletItem
Enclose entry details between
\CodeCommand{begin\{Detail\}} and
\CodeCommand{end\{Detail\}}
so that they are typeset in a smaller font.
\begin{Detail}
\Item
This is an example of entry detail text enclosed in a \Code{Detail} environment.
\end{Detail}

\Gap
\BulletItem
Use \CodeCommand{Gap} and \CodeCommand{BigGap} to insert vertical spaces between entries to improve layout.

\BigGap
\SubSection
{This is Another SubSection}
{This is Another Subsection (For PDF Bookmark)}
{PDF:ThisIsAnotherSubSection:ForPDFLink}

\Gap
\Entry
This is a plain \CodeCommand{Entry},
followed by an \CodeCommand{hfill} and a date range
\hfill
\DatestampYM{2015}{10} --
\DatestampYM{2015}{12}

\Gap
\BulletItem
This is a \CodeCommand{BulletItem}.
\Item
This is an \CodeCommand{Item}, which has no bullet.
Note the alignment with the \CodeCommand{BulletItem} above.

\Gap
\SubBulletItem
This is a \CodeCommand{SubBulletItem}.
\SubItem
This is a \CodeCommand{SubItem}, which has no bullet.
Note the alignment with the \CodeCommand{SubBulletItem} above.

\Gap
\NumberedItem{[42]}
This is a \CodeCommand{NumberedItem}.
Change the value of the macro \CodeCommand{MaxNumberedItem} to adjust the indentation width.

\BigGap
\SubSection
{Line, Paragraph, and Page Breaks}
{Line, Paragraph, and Page Breaks (For PDF Bookmark)}
{PDF:LineParagraphAndPageBreaks:ForPDFLink}

\Gap
\BulletItem
To create a new line within the same paragraph (i.e., preserving the same paragraph indentation), use \CodeCommand{newline} instead of \CodeCommand{\textbackslash};
the latter will reset the paragraph indentation.

\Gap
\BulletItem
To create a new paragraph, use \CodeCommand{par} or simply leave an empty line.
Paragraph indentations (from
\CodeCommand{Entry},
\CodeCommand{BulletItem},
\CodeCommand{SubBulletItem},
\CodeCommand{Item},
\CodeCommand{SubItem},
\CodeCommand{NumberedItem},
etc.) do not carry across different paragraphs.

\Gap
\BulletItem
To create a new page, use \CodeCommand{newpage}.

\BigGap
\SubSection
{Dates}
{Dates (For PDF Bookmark)}
{PDF:Dates:ForPDFLink}

\Gap
\BulletItem
Use the following macros to specify and display dates consistently:
\SubBulletItem
\CodeCommand{DatestampYMD\{yyyy\}\{MM\}\{dd\}}
(e.g., \CodeCommand{DatestampYMD\{2008\}\{01\}\{15\}})
\SubBulletItem
\CodeCommand{DatestampYM\{yyyy\}\{MM\}}
(e.g., \CodeCommand{DatestampYM\{2008\}\{01\}})
\SubBulletItem
\CodeCommand{DatestampY\{yyyy\}}
(e.g., \CodeCommand{DatestampY\{2008\}})

\Gap
\BulletItem
Change the date format option passed to the document class to adjust how dates are displayed throughout the document:
\SubBulletItem
\Code{MMMyyyy} (``Jan~2008'')
\SubBulletItem
\Code{ddMMMyyyy} (``15~Jan~2008'')
\SubBulletItem
\Code{MMMMyyyy} (``January~2008'')
\SubBulletItem
\Code{ddMMMMyyyy} (``15~January~2008'')
\SubBulletItem
\Code{yyyyMMdd} (``2008-01-15'')
\SubBulletItem
\Code{yyyyMM} (``2008-01'')
\SubBulletItem
\Code{yyyy} (``2008'')

\endgroup

\end{comment}

\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

%\UseNoteFont%
%\null\hfill%
%[\textit{\CVNote}]

\end{document}
